visitation_bias

### 2021-01-28 code/visitation_bias.Rmd
back to lappy

# 2. Explaining bias
## 2.1 Calculate visitation probability per plant speces/ktype/family
```{r}
pvis_ktype <- visit_cover %>%
  group_by(site, date, bb.sp, plant.sp) %>%
  summarize(flower.cover = sum(flower.cover), # get raw flower cover and visits by site*date*bb.sp*plant.sp
            visits = sum(visits)) %>%
  group_by(site, date) %>%
  mutate(prop.flower.cover = flower.cover/sum(flower.cover), # proportional flower cover
         prop.visits = visits/sum(visits), # proportional visits
         visits.bin = factor(if_else(visits > 0, 1, 0))) %>% # binary visits
  group_by(site, date, bb.sp) %>%
  mutate(bb.sp.abund = sum(visits)) %>% # abundance of each BB sp. per site-date
  ungroup() %>%
  left_join(fl_traits) %>% # add floral traits
  left_join(bb_traits) %>% # add BB traits
  mutate(k.type.ss = factor(k.type.ss), # recode variables
         pbl.w.class2 = factor(pbl.w.class2),
         visits = as.integer(visits)) %>%
  filter(!k.type.ss %in% c("9", "10")) %>% # Drop ktypes 9 and 10 since both are extremely rare
  left_join(site_data)  %>%
  mutate(prop.flower.cover0 = scale(prop.flower.cover), # normalized predictors
         bb.sp.abund0 = scale(bb.sp.abund),
         elev.mean0 = scale(elev.mean),
         yday = yday(date), # and add yday variable
         yday0 = scale(yday)) %>%
  select(site, elev.mean0, elev.mean, elev.class2, date, yday, yday0, bb.sp, plant.sp, visits, 
         visits.bin, prop.visits, prop.flower.cover, prop.flower.cover0,
         k.type.ss, bb.sp.abund, bb.sp.abund0, pbl.w.class2) 
```

## 2.2 Multi-level models

### 2.2.1 Preliminary visualization
The tons of zeros are due to the lots of plant species that were present at very low abundance and received few or zero visits. This might not be ideal. We could opt for one of our alternative bias measure, like fold change, which all give something like a poisson distribution, but I don't know if this would be an improvement. We could also filter our data to include only plants that were above some threshold of relative abundance, say, 1%.
```{r}
# Visit.prop
ggplot(filter(pvis_ktype, prop.flower.cover >= 0.05), aes(prop.visits)) +
  geom_histogram()

# Visits.bin
ggplot(pvis_ktype, aes(k.type.ss, fill = visits.bin)) +
  geom_bar()

ggplot(pvis_ktype, aes(elev.mean, prop.visits)) +
  geom_point() +
  geom_smooth() +
  facet_grid(bb.sp~k.type.ss)

# Visits.bin filtered
ggplot(filter(pvis_ktype, prop.flower.cover >= 0.05), aes(k.type.ss, fill = visits.bin)) +
  geom_bar()
```

### 2.2.2 brms models
```{r}
# Zero- one-inflated beta regression
brm_pvis01 <- brm(prop.visits ~ prop.flower.cover0 + 
                    (1 | k.type.ss) + 
                    (1 | site) + 
                    (1 | bb.sp),
                  family = "zero_one_inflated_beta",
                  file = "./output/brm_pvis01",
                  chains = 4,
                  cores = 4,
                  iter = 2000,
                  data = pvis_ktype)

# Poisson models of raw visit counts
brm_pvis00 <- brm(visits ~ prop.flower.cover0 + 
                    bb.sp.abund0 + 
                    (1 | k.type.ss) + 
                    (1 | site) + 
                    (1 | bb.sp),
                  #control = list(adapt_delta = 0.99),
                  family = "poisson",
                  file = "../output/brm_pvis00",
                  chains = 4,
                  #cores = 4,
                  iter = 2000,
                  data = pvis_ktype)

summary(brm_pvis00)
prior_summary(brm_pvis00)
parnames(brm_pvis00)
mcmc_plot(brm_pvis00, pars = c("^r_k"))
mcmc_plot(brm_pvis00, pars = c("^r_s"))
mcmc_plot(brm_pvis00, pars = c("^b_"))
mcmc_plot(brm_pvis00)
conditional_effects(brm_pvis00)
pp_check(brm_pvis00)
bayes_R2(brm_pvis00)

# Perhaps I should add the bb.sp varying intercept effect; otherwise, I think I could be accused of pseudo replication.
brm_pvis11 <- brm(visits ~ prop.flower.cover0 + 
                    bb.sp.abund0 + 
                    (1 | k.type.ss:pbl.w.class2) + 
                    (1 | site) +
                    (1 | bb.sp),
                  family = "poisson",
                  file = "../output/brm_pvis11",
                  chains = 4,
                  #cores = 4,
                  iter = 2000,
                  data = pvis_ktype)

summary(brm_pvis11)
prior_summary(brm_pvis11)
parnames(brm_pvis11)
mcmc_plot(brm_pvis11, pars = c("^r_k"))
mcmc_plot(brm_pvis11, pars = c("^r_b"))
mcmc_plot(brm_pvis11, pars = c("^b_"))
mcmc_plot(brm_pvis11)
conditional_effects(brm_pvis11)
pp_check(brm_pvis11)
bayes_R2(brm_pvis11)
```

@@

## Interaction model
brm_pvis11_plotframe <- brm_pvis11 %>%
  spread_draws(b_Intercept, `r_k.type.ss:pbl.w.class2`[condition, term]) %>% # the back ticks are necessary to escape the :
  rename(r_ktype.pbl = `r_k.type.ss:pbl.w.class2`) %>%
  mutate(condition_mean = b_Intercept + r_ktype.pbl) %>%
  separate(condition, c("ktype", "pbl.class"), sep = "_", remove = FALSE) %>%
  mutate(pbl.class = case_when(
    pbl.class == "1" ~ "short",
    pbl.class == "2" ~ "med",
    pbl.class == "3" ~ "long")
    ) %>%
  mutate(ktype = case_when(
    ktype == "0" ~ "NA (0)",
    ktype == "1" ~ "Disc (1)",
    ktype == "2" ~ "Funnel (2)",
    ktype == "3" ~ "Bell (3)",
    ktype == "4" ~ "Stalk-disc (4)",
    ktype == "5" ~ "Lip (5)",
    ktype == "6" ~ "Flag (6)",
    ktype == "7" ~ "Head (7)")
  ) %>%
  mutate(ktype = factor(ktype,
                        levels = c("Disc (1)", "Funnel (2)", "Bell (3)", "Stalk-disc (4)",
                                   "Lip (5)", "Flag (6)", "Head (7)", "NA (0)")))

@@

ggplot(brm_pvis11_plotframe, aes(condition_mean, pbl.class, color = pbl.class, fill = pbl.class)) +
  #stat_pointinterval() +
  stat_halfeye(alpha = 0.4, interval_alpha = 1, point_alpha = 1) +
  facet_wrap(~ktype, scales = "free") +
  theme_light() +
  labs(color = "Tongue length", x = "Visits (log-scale)") +
  guides(fill = FALSE) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

@@

### 2.2.3 The lability of bias: How does the foraging bias of each species with respect to each morphotype vary through elevation and time?
```{r}
ggplot(pvis_ktype, aes(elev.mean, prop.visits)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 5)) +
  facet_grid(bb.sp ~ k.type.ss)

>>>>

# 2. Explaining bias
## 2.1 Calculate visitation probability per plant morphotype. Instead of keeping the plant species resolved, we will pool visitation by morphotype. The problem with not pooling by morphotype is that more species-rich morphotypes will be penalized simply because their visitation is diluted across more species.
```{r}
pvis_ktype <- visit_cover %>%
  group_by(site, date, bb.sp, k.type.ss) %>%
  summarize(flower.cover = sum(flower.cover), # get raw flower cover and visits by site*date*bb.sp*plant.sp
            visits = sum(visits)) %>%
  group_by(site, date) %>%
  mutate(prop.flower.cover = flower.cover/sum(flower.cover), # proportional flower cover
         prop.visits = visits/sum(visits), # proportional visits
         visits.bin = factor(if_else(visits > 0, 1, 0))) %>% # binary visits
  group_by(site, date, bb.sp) %>%
  mutate(bb.sp.abund = sum(visits)) %>% # abundance of each BB sp. per site-date
  ungroup() %>%
  left_join(bb_traits) %>% # add BB traits
  mutate(k.type.ss = factor(k.type.ss), # recode variables
         pbl.w.class2 = factor(pbl.w.class2),
         visits = as.integer(visits)) %>%
  filter(!k.type.ss %in% c("9", "10")) %>% # Drop ktypes 9 and 10 since both are extremely rare
  left_join(site_data)  %>%
  ungroup() %>%
  mutate(prop.flower.cover0 = scale(prop.flower.cover), # normalized predictors
         bb.sp.abund0 = scale(bb.sp.abund),
         elev.mean0 = scale(elev.mean),
         yday = yday(date), # and add yday variable
         yday0 = scale(yday)) %>%
  select(site, elev.mean0, elev.mean, elev.class2, date, yday, yday0, 
         bb.sp, k.type.ss, visits, visits.bin, prop.visits, prop.flower.cover, 
         prop.flower.cover0, bb.sp.abund, bb.sp.abund0, pbl.w.class2)

write_csv(pvis_ktype, "../hpc_packets/pvis_ktype.csv")

# We can also pool across BB spp. to focus just on how much visitation each ktype gets
pvis_ktype_pool <- visit_cover %>%
  group_by(site, date, k.type.ss) %>%
  summarize(flower.cover = sum(flower.cover), # get raw flower cover and visits by site*date*bb.sp*plant.sp
            visits = sum(visits)) %>%
  group_by(site, date) %>%
  mutate(prop.flower.cover = flower.cover/sum(flower.cover), # proportional flower cover
         prop.visits = visits/sum(visits), # proportional visits
         visits.bin = factor(if_else(visits > 0, 1, 0))) %>% # binary visits
  group_by(site, date) %>%
  mutate(bb.abund = sum(visits)) %>% # abundance of each BB sp. per site-date
  ungroup() %>%
  mutate(k.type.ss = factor(k.type.ss), # recode variables
         visits = as.integer(visits)) %>%
  filter(!k.type.ss %in% c("9", "10")) %>% # Drop ktypes 9 and 10 since both are extremely rare
  left_join(site_data)  %>%
  ungroup() %>%
  mutate(prop.flower.cover0 = scale(prop.flower.cover), # normalized predictors
         bb.abund0 = scale(bb.abund),
         elev.mean0 = scale(elev.mean),
         yday = yday(date), # and add yday variable
         yday0 = scale(yday)) %>%
  select(site, elev.mean0, elev.mean, elev.class2, date, yday, yday0, 
         k.type.ss, visits, visits.bin, prop.visits, prop.flower.cover, 
         prop.flower.cover0, bb.abund, bb.abund0)

pvis_ktype_sitepool <- pvis_ktype %>%
  group_by(site, elev.mean, bb.sp, pbl.w.class2, k.type.ss) %>%
  summarize(mean.prop.visits = mean(prop.visits),
            mean.prop.flower.cover = mean(prop.flower.cover))

pvis_ktype_sitepool2 <- pvis_ktype %>%
  group_by(site, elev.mean, bb.sp, pbl.w.class2, k.type.ss) %>%
  summarize(mean.prop.visits = weighted.mean(prop.visits, bb.sp.abund),
            mean.prop.flower.cover = mean(prop.flower.cover))

ggplot(pvis_ktype_sitepool, aes(mean.prop.flower.cover, mean.prop.visits)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~k.type.ss)

ggplot(pvis_ktype_sitepool, aes(mean.prop.visits)) +
  geom_histogram() +
  facet_grid(pbl.w.class2~k.type.ss)

ggplot(pvis_ktype_sitepool2, aes(mean.prop.visits)) +
  geom_histogram() +
  facet_grid(pbl.w.class2~k.type.ss)
```

## 2.2 Multi-level models
### I think the structure of my data necessitates a complex model design. My observations of prop.visits ~ pbl.w.class:k.type.ss are repeated within BB species, and therefore not independent. Moreover, my observations are repeated within sites, adding another layer of non-independence. I think this means I need to include varying intercept terms for both BB sp and site. 
### I did some visualization, and it is also clear that the slope of prop.visits ~ prop.flower.cover varies strongly with pbl.w.class:ktype. This is very informative, and it makes good sense. 
```{r}
brm_pvis62 <- brm(mean.prop.visits ~ mean.prop.flower.cover + 
                    (1 + mean.prop.flower.cover | k.type.ss:pbl.w.class2) + 
                    (1 + mean.prop.flower.cover | k.type.ss:bb.sp),
                  family = "zero_one_inflated_beta",
                  file = "../output/brm_pvis62",
                  #file = "brm_pvis61",
                  chains = 4,
                  cores = 4,
                  iter = 2000,
                  data = pvis_ktype_sitepool2)
bayes_R2(brm_pvis62)

brm_pvis61 <- brm(mean.prop.visits ~ mean.prop.flower.cover + 
                    (1 + mean.prop.flower.cover | k.type.ss:pbl.w.class2) + 
                    (1 + mean.prop.flower.cover | k.type.ss:bb.sp),
                  family = "zero_one_inflated_beta",
                  file = "../output/brm_pvis61",
                  #file = "brm_pvis61",
                  chains = 4,
                  cores = 4,
                  iter = 2000,
                  data = pvis_ktype_sitepool)

summary(brm_pvis61)
prior_summary(brm_pvis61)
parnames(brm_pvis61)
mcmc_plot(brm_pvis61, pars = c("^r_k"))
mcmc_plot(brm_pvis61, pars = c("^r_s"))
mcmc_plot(brm_pvis61)
conditional_effects(brm_pvis61)
pp_check(brm_pvis61)
bayes_R2(brm_pvis61)
mcmc_plot(brm_pvis50, pars = c("r_k.type.ss:pbl.w.class2[0_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[0_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[0_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[1_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[1_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[1_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[2_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[2_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[2_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[3_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[3_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[3_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[4_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[4_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[4_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[5_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[5_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[5_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[6_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[6_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[6_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[7_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[7_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[7_3,prop.flower.cover0]"),
          fixed = TRUE)

mcmc_plot(brm_pvis50, pars = c("r_k.type.ss:pbl.w.class2[0_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[0_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[0_3,Intercept]",
                               "r_k.type.ss:pbl.w.class2[1_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[1_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[1_3,Intercept]",
                               "r_k.type.ss:pbl.w.class2[2_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[2_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[2_3,Intercept]",
                               "r_k.type.ss:pbl.w.class2[3_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[3_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[3_3,Intercept]",
                               "r_k.type.ss:pbl.w.class2[4_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[4_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[4_3,Intercept]",
                               "r_k.type.ss:pbl.w.class2[5_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[5_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[5_3,Intercept]",
                               "r_k.type.ss:pbl.w.class2[6_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[6_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[6_3,Intercept]",
                               "r_k.type.ss:pbl.w.class2[7_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[7_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[7_3,Intercept]"),
          fixed = TRUE)

brm_pvis60 <- brm(prop.visits ~ prop.flower.cover0 + 
                    (1 + prop.flower.cover0 | k.type.ss:pbl.w.class2) + 
                    (1 + prop.flower.cover0 | k.type.ss:site) +
                    (1 + prop.flower.cover0 | k.type.ss:bb.sp),
                  family = "zero_one_inflated_beta",
                  file = "../output/brm_pvis60",
                  #file = "brm_pvis60",
                  chains = 4,
                  cores = 4,
                  iter = 2000,
                  data = pvis_ktype)
bayes_R2(brm_pvis60)
conditional_effects(brm_pvis60)
mcmc_plot(brm_pvis60, pars = c("^b_"))
mcmc_plot(brm_pvis60, pars = c("r_k.type.ss:pbl.w.class2[0_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[0_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[0_3,Intercept]",
                               "r_k.type.ss:pbl.w.class2[1_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[1_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[1_3,Intercept]",
                               "r_k.type.ss:pbl.w.class2[2_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[2_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[2_3,Intercept]",
                               "r_k.type.ss:pbl.w.class2[3_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[3_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[3_3,Intercept]",
                               "r_k.type.ss:pbl.w.class2[4_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[4_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[4_3,Intercept]",
                               "r_k.type.ss:pbl.w.class2[5_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[5_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[5_3,Intercept]",
                               "r_k.type.ss:pbl.w.class2[6_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[6_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[6_3,Intercept]",
                               "r_k.type.ss:pbl.w.class2[7_1,Intercept]",
                               "r_k.type.ss:pbl.w.class2[7_2,Intercept]",
                               "r_k.type.ss:pbl.w.class2[7_3,Intercept]"),
          fixed = TRUE)
mcmc_plot(brm_pvis60, pars = c("r_k.type.ss:pbl.w.class2[0_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[0_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[0_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[1_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[1_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[1_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[2_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[2_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[2_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[3_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[3_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[3_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[4_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[4_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[4_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[5_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[5_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[5_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[6_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[6_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[6_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[7_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[7_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[7_3,prop.flower.cover0]"),
          fixed = TRUE)

brm_pvis50 <- brm(prop.visits ~ prop.flower.cover0 + 
                    (1 + prop.flower.cover0 | k.type.ss:pbl.w.class2) + 
                    (1 | k.type.ss:site) +
                    (1 | k.type.ss:bb.sp),
                  family = "zero_one_inflated_beta",
                  file = "../output/brm_pvis50",
                  #file = "brm_pvis50",
                  chains = 4,
                  cores = 4,
                  iter = 2000,
                  data = pvis_ktype)

summary(brm_pvis50)
prior_summary(brm_pvis50)
get_variables(brm_pvis50)
mcmc_plot(brm_pvis50, pars = c("r_k.type.ss:pbl.w.class2[2_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[2_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[2_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[3_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[3_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[3_3,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[6_1,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[6_2,prop.flower.cover0]",
                               "r_k.type.ss:pbl.w.class2[6_3,prop.flower.cover0]"),
          fixed = TRUE)

mcmc_plot(brm_pvis50, pars = c("r_k.type.ss:bb.sp[3_gers,Intercept]",
                               "r_k.type.ss:bb.sp[3_hort,Intercept]",
                               "r_k.type.ss:bb.sp[3_hypn,Intercept]",
                               "r_k.type.ss:bb.sp[3_humi,Intercept]",
                               "r_k.type.ss:bb.sp[3_jone,Intercept]",
                               "r_k.type.ss:bb.sp[3_lapi,Intercept]",
                               "r_k.type.ss:bb.sp[3_mend,Intercept]",
                               "r_k.type.ss:bb.sp[3_mont,Intercept]",
                               "r_k.type.ss:bb.sp[3_muci,Intercept]",
                               "r_k.type.ss:bb.sp[3_pasc,Intercept]",
                               "r_k.type.ss:bb.sp[3_prat,Intercept]",
                               "r_k.type.ss:bb.sp[3_psit,Intercept]",
                               "r_k.type.ss:bb.sp[3_pyre,Intercept]",
                               "r_k.type.ss:bb.sp[3_soro,Intercept]",
                               "r_k.type.ss:bb.sp[3_telu,Intercept]",
                               "r_k.type.ss:bb.sp[3_wurf,Intercept]"),
          fixed = TRUE)

mcmc_plot(brm_pvis50, pars = c("r_k.type.ss:bb.sp[6_gers,Intercept]",
                               "r_k.type.ss:bb.sp[6_hort,Intercept]",
                               "r_k.type.ss:bb.sp[6_hypn,Intercept]",
                               "r_k.type.ss:bb.sp[6_humi,Intercept]",
                               "r_k.type.ss:bb.sp[6_jone,Intercept]",
                               "r_k.type.ss:bb.sp[6_lapi,Intercept]",
                               "r_k.type.ss:bb.sp[6_mend,Intercept]",
                               "r_k.type.ss:bb.sp[6_mont,Intercept]",
                               "r_k.type.ss:bb.sp[6_muci,Intercept]",
                               "r_k.type.ss:bb.sp[6_pasc,Intercept]",
                               "r_k.type.ss:bb.sp[6_prat,Intercept]",
                               "r_k.type.ss:bb.sp[6_psit,Intercept]",
                               "r_k.type.ss:bb.sp[6_pyre,Intercept]",
                               "r_k.type.ss:bb.sp[6_soro,Intercept]",
                               "r_k.type.ss:bb.sp[6_telu,Intercept]",
                               "r_k.type.ss:bb.sp[6_wurf,Intercept]"),
          fixed = TRUE)

mcmc_plot(brm_pvis50, pars = c("^r_k.type.ss:site"))
mcmc_plot(brm_pvis50)
conditional_effects(brm_pvis50)
pp_check(brm_pvis50)
bayes_R2(brm_pvis50)

## BB spp. pooled, only interested in comparing ktypes here
brm_pvis12 <- brm(prop.visits ~ prop.flower.cover0 + 
                    (1 | k.type.ss) + 
                    (1 | site),
                  family = "zero_one_inflated_beta",
                  file = "../output/brm_pvis12",
                  #file = "brm_pvis12",
                  chains = 4,
                  cores = 4,
                  iter = 2000,
                  data = pvis_ktype_pool)

summary(brm_pvis12)
prior_summary(brm_pvis12)
parnames(brm_pvis12)
mcmc_plot(brm_pvis12, pars = c("^r_k"))
mcmc_plot(brm_pvis12, pars = c("^r_s"))
mcmc_plot(brm_pvis12)
conditional_effects(brm_pvis12)
pp_check(brm_pvis12)
bayes_R2(brm_pvis12)

```{r}
# mgcv time
gam1 <- bam(prop.visits ~ prop.flower.cover0 +
              te(yday, elev.mean, by = k.type.ss, bs = c("gp", "tp"), k = c(8, 8)),
            family = "betar",
            method = "fREML",
            discrete = TRUE,
            data = pvis_ktype_pool) %>% getViz()

summary(gam1)
check.gamViz(gam1)
plot.gamViz(gam1)

gam2 <- bam(visits ~ te(yday, elev.mean, by = k.type.ss, bs = c("gp", "tp"), k = c(8, 8)),
            family = "quasipoisson",
            method = "fREML",
            discrete = TRUE,
            data = pvis_ktype_pool) %>% getViz()

summary(gam2)
check.gamViz(gam2)
plot.gamViz(gam2)

@@

## Interaction model
brm_pvi50_plotframe <- brm_pvis50 %>%
  spread_draws(b_Intercept, `r_k.type.ss:pbl.w.class2`[condition, term]) %>% # the back ticks are necessary to escape the :
  rename(r_ktype.pbl = `r_k.type.ss:pbl.w.class2`) %>%
  mutate(condition_mean = b_Intercept + r_ktype.pbl) %>%
  mutate(condition_mean = inv_logit_scaled(condition_mean)) %>%
  separate(condition, c("ktype", "pbl.class"), sep = "_", remove = FALSE) %>%
  mutate(ktype = case_when(
    ktype == "0" ~ "NA (0)",
    ktype == "1" ~ "Disc (1)",
    ktype == "2" ~ "Funnel (2)",
    ktype == "3" ~ "Bell (3)",
    ktype == "4" ~ "Stalk-disc (4)",
    ktype == "5" ~ "Lip (5)",
    ktype == "6" ~ "Flag (6)",
    ktype == "7" ~ "Head (7)")
  ) %>%
  mutate(ktype = factor(ktype,
                        levels = c("Disc (1)", "Funnel (2)", "Bell (3)", "Stalk-disc (4)",
                                   "Lip (5)", "Flag (6)", "Head (7)", "NA (0)")))

@@

ggplot(brm_pvi50_plotframe, aes(condition_mean, pbl.class, color = pbl.class, fill = pbl.class)) +
  #stat_pointinterval() +
  stat_halfeye(alpha = 0.4, interval_alpha = 1, point_alpha = 1) +
  facet_wrap(~ktype, scales = "free") +
  theme_light() +
  labs(color = "Tongue length", x = "Visits (log-scale)") +
  guides(fill = FALSE) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

@@

### 2.2.3 The lability of bias: How does the foraging bias of each species with respect to each morphotype vary through elevation and time?

#### We need to do some kind of tensor product gam on this jawn!
```{r}
ggplot(pvis_ktype_pool, aes(yday, elev.mean, color = prop.visits)) +
  geom_point() +
  facet_wrap(~k.type.ss)
```

```{r}
ggplot(pvis_ktype, aes(elev.mean, prop.visits)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 5)) +
  facet_grid(bb.sp ~ k.type.ss)
